---
title: "Lab 8 - 11/15"
author: "Chase Tarr"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attaching packages

library(tidyverse)
library(stargazer)
library(corrplot)
library(broom)
library(modelsummary)
library(here)
```

## Reading in the data
```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```
 Use `unique(homes$City)` to see how many different entries there are in that column
 
A littl bit of cleaning:

- make a subset called homes_sub that only contains observations (rows) where the city is:
  - San Luis Obispo
  - Arroyo Grande
  - Atascadero
  - Santa Maria-Orcutt
  
```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```
 - using `unique(homes_sub$City)` to make sure the output is correct of new data frame for City column
 
## Doing a little exploring of our data

- Summary statistics for home price based on city and sale status: 

Find and return in a nice summary table the mean and standard deviation of homeprice grouped by city and sale status
```{r}
summary_table <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE), # removes the NA values
            sd_price = sd(Price, na.rm = TRUE))

# actually i dont even want to run this code: eval = FALSE in the top

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +# alpha outside aes() because only things that are related to variable goes in the aes
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship (visual data exploration) between square footage and home price.

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price))+
  geom_point(aes(color = City, fill = City, shape = Status), alpha = 0.7)+ # using color, fill and shape to identify differences in houses
  geom_smooth(method = lm)
```





