---
title: "Lab 8 - 11/15"
author: "Chase Tarr"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attaching packages

library(tidyverse)
library(stargazer)
library(corrplot)
library(broom)
library(modelsummary)
library(here)
```

## Reading in the data
```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```
 Use `unique(homes$City)` to see how many different entries there are in that column
 
A littl bit of cleaning:

- make a subset called homes_sub that only contains observations (rows) where the city is:
  - San Luis Obispo
  - Arroyo Grande
  - Atascadero
  - Santa Maria-Orcutt
  
```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```
 - using `unique(homes_sub$City)` to make sure the output is correct of new data frame for City column
 
## Doing a little exploring of our data

- Summary statistics for home price based on city and sale status: 

Find and return in a nice summary table the mean and standard deviation of homeprice grouped by city and sale status
```{r}
summary_table <- homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE), # removes the NA values
            sd_price = sd(Price, na.rm = TRUE))

# actually i dont even want to run this code: eval = FALSE in the top

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +# alpha outside aes() because only things that are related to variable goes in the aes
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship (visual data exploration) between square footage and home price.

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price))+
  geom_point(aes(color = City, fill = City, shape = Status), alpha = 0.7)+ # using color, fill and shape to identify differences in houses
  geom_smooth(method = lm)
```

## Model the relationship with home price as the DV

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# make a subset that only contains the quantitative variables
homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt) # omitting city becuase cant check correlation between categorical variables

homes_cor <- cor(homes_quant)

corrplot(homes_cor)

homes_cor

homes_lm1

# how would I explore the diagnostic plots

plot(homes_lm1)
```

- if everthing else is held constant, on average, I would expect a house in Atascadero to cost $9068.20 less than a house in Arroyo Grande

Try another model where we simplify this a bit:

- City 
- SqFt
- Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)

# or just call this in the console if you wanna take a look
homes_lm2

plot(homes_lm2)

summary(homes_lm1)
```

the adjusted r-squared value: 84% of the variance in home price is explained by the predictor variables in this model (City, Bedrooms, Bathrooms, Price per sq foot, Status and Sq footage). the other 16% would be from outside variables such as property size or location / updated inside / renovations

```{r}
summary(homes_lm2)
```

Find the AIC value of each model:
 - lower values = better fit and complexity
```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```


Try another permutation of this model that you think might make sense, check out and compare the model fit, outputs, and AIC value

```{r}
homes_lm3 <- lm(Price ~ City + PricePerSqFt + Bedrooms + Status, data = homes_sub)

summary(homes_lm3)

AIC(homes_lm3)
```


Use `modelsummary` to show model outputs side-by-side:

 - if you use modelsummary to return model outputs of multiple models, it wants you to feed it to it as a list.
```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))

# goood to compare across different models to see what values make sense with world knowledge and realistically 
# standard errors are in parenthesis below the values in the summary sheet when knitted
```

## Start making predictions with this model

use `broom::augment()`

```{r}
homes_predicted <- augment(homes_lm1)

homes_predicted
```

Use predict function to try out your model on new scenarios that you create


